%\chapter{1994}
\section{Items}
\begin{enumerate}
%page 1
\item A little league baseball team, at least 9 members, must be in uniform (99 pts)$\dagger$
\item The signature of a college advisor on a team member's bare buttocks (30 pts)
\item What is the size of the tires on the tank in Foster Park, Kokomo? (6 pts)
\item Someone reading a page of their olders sister's diary (7 pts)
\item A full size automobile door with operational roll-up window, removed from the auto (68 pts)
\item A rugby scrum (13 pts)
\item A copy of the Ann Landers column that advocated masturbation (20 pts)
\item An auxiliary nipple (33 pts)
\item Spontaneous combustion (11 pts)$\dagger$
\item Proof that Elvis is alive and Paul McCartney is dead (8 pts)
\item A bright green pen from Herrin Bowl bowling alley (10 pts plus the number of points you get on the next two items)
\item Which platoon is based out of the Indiana National Guard Amory in Monticello? (6 pts)
\item A preserved brain, in a jar (13 pts)
\item A positive pregnancy test (28)
\item Someone with a different color of nail polish on each of ten fingers and ten toes, must have twenty noticeably different colors (20 pts)
\item A copy of Kurt's suicide note (27 pts)
\item Someone putting five toes of somone else's foot in their mouth (5 pts)
\item Write a poem about the University's financial woes, including the names of at least three relevant administrators. Make it good. (6 pts for a haiku, 9 for a limerick, 14 for a sonnet, and 25 pts for all three)
\item Someone to successfully ``bob'' for pickles in a pickle barrel, barrel must be at least 5 gallons and have at least 5 pickles in it (30 pts)$\dagger$
\item An official {\UofC} degree certificate without recipient's name and degree on it (19 pts)
\item A fresh eucalyptus leaf (17 pts)
\item Someone eating 50 Pixie stix{\texttrademark} in a minute (15 pts)
\item A Garden Weasel{\texttrademark} (15 pts, + 5 bonus pts if you show how easy it is to clean)$\dagger$
\item A ceiling fan (23 pts)
\item A rostrum (31 pts)
\item an empty Guinness Gold{\texttrademark} bottle (21 pts)
\item Verification from the Children's Television Workshop that Ernie is neither gay nor dead (This item is brought you by the letters ``B,'' ``M,'' and the number ``27'')
\item A conspiracy theory connecting Atlantis, the Bavarian Illuminati, crop circles, the Hope Diamond curse, the Egyptian pyramids and the University of Chicago (5-13 pts, judge's discretion)
\item Musca domestica frozen in an ice cube (10 pts)
\item The number of electrical outlets in Pick 419? (4 pts)
\item An alpenhorn (61 pts)
\item Blood: donate blood to United Blood Services on Friday, May 6th, either in the North Lounge of Reynolds Club from 9:30am to 4:30pm or in the Bloodmobile in Hutchinson Court from 10:00am to 7:00pm, judges will record donations (25 pts per, max. 500 pts)
\item A key that says ``do not duplicate'' and a copy of it (8 pts)
\item Anything with the Indiana Convention Center \& Hoosier Dome {\it logo} on it (16 pts)
\item An English translation of the Quenya Elvish phrase ``T\'valve hosta nation'' or of the Klingon phrase ``DItu' Dochmey law' ''(15 pts)
\item What is the type and sex of the tree in front of the Frank Lloyd Wright Home and Studio Bookstore in Oak Park, IL? (3 pts)
\item A rubbing of hte 50's actor James B. Dean's tombstone (24 pts)
\item How many fish are in the aquarium at 57th Street Salon? (5 pts)
\item A chessboard recreating the game position in Sylvia Sleigh's ``Nancy Speo, Leon Golub and Sons Stepson, Phillip and Paul'' in the Smart Museum of Art. (16 pts)
\item (20 pts)%FIND AND ADD IMAGES

%page 2
\item Who was the college roommate of Indiana Jones at the University of Chicago, according to ``The Young Indiana Jones Chornicles''? (2 pts)
\item A plectrum (5 pts)
\item What book is recorded by ISBN 0-8362-1735-7 (5 pts)
\item An IHOP waitress, in uniform (50 pts)
\item Somone to interpret what the judge signs in American Sign Language (14 pts)
\item An adiaphanous rubicund conglobulate inside a semipellucid glaucous poke (18 pts)
\item A virtual image of a purple cow (19 pts)
\item Team member with his/her: nose to the grindstone, shoulder to the wheel, hands on the plow, eye on the prize, feet on the ground, and back to the wall (36 pts)
\item A leap of faith (10 pts)
\item Who is eligible to recieve the A. Royal Gay University of Chicago scholarship? (7 pts)
\item Certification that a team member has completed one lap around the Indianapolis ``500'' Mile Speedway (20 pts)
\item What is the capacity in gallons of the reservoir in the Illinois Central Railroad Engine in Paducah? (16 pts)
\item $\pi$ recited to 50 digits from memory (31 pts)
\item An Olympic medal and the athlete who won it (122 pts for gold, 121 pts for silver, 120 pts for bronze)
\item A contraceptive diaphragm (16 years ol{\dots}I mean pts)
\item A copy of the inscription below the cannon in Energy, IL. (13 pt)
\item A holy grail (3pts. No more, no less. Three shall be the number of the points and the number of the points shall be three. The points shall not be four{\dots})
\item A brick from teh Chicago Brick Company with union mark (35 pts)
\item An unbreakable comb, broken (9 pts)
\item A lawn gnome (17 pts)
\item A pack each of Fruit Stripe{\texttrademark}, Cinn-A-Burst{\texttrademark}, and Clove{\texttrademark} gum and five pieces of Eye Poppers{\texttrademark} all chewed simultaneously by the same person (25 pts)
\item Knickers and knockers on the same person (36 pts)
\item A pair of orange coveralls resembling a prisoner's uniform (23 pts)
\item A newel post (16 pts)
\item Chicago police ``Movie Location - No Parking'' sign (13 pts)
\item A gospel pamphlet warning about the end of the world (6 pts)
\item A man, a woman, a live snake, a red apple, leaves, {\it nothing else} (69 pts)
\item Where was the Crerar library originally? (3 pts)
\item 20 live crickets in a ``Going Fishing with Crickets'' container with receipt from Handi-Corner Live Bait in Central City, KY (20 pts)
\item Someone with a genuine handlebar mustache, waxed (8 pts)
\item A Unification Church leaflet mentioning the Reverend Sun Hyung Moon by name (5 pts)
\item A bust of Lenin or Marx (30 pts)
\item What is the number on the fare register in the Chicago Historical Socity, History of Chicago Exhibit? (5 pts)
\item A Barbie{\texttrademark} doll, covered with honey, buried up to its neck in an ant farm filled with live ants (38 pts)
\item Logan School in Hanaford, IL---Home of the \rule{.5in}{.01in}?(10 pts)
\item A 1/2 order of biscuits and gravy from Dolly's Place Restaurant in Vienna, extra points if you find out where Sam sits (20 pts, 10 bonus)
\item Recite from memory what is written on top of the Altar of Consecration in the Indiana War Memorial, Indianapolis (19 pts)
\item An underwear drawer, just as you found it (16 pts)
\item A figment of  your imagination (8 pts)
\item Who is the Mayor of Greensburg? (5 pts)

%page 3
\item What is the tallest bank building in the world? (2 pts)
\item A Mike Royko article translated into Pig Latin with his secretary's signature on it. (54 pts)
\item A stub from a bet placed at Churchill Downs (10 pts)
\item Two US Marines, in uniform, to properly fold a U.S. flag (50 pts)
\item Who would assume the office of Presidency of the United States in the event of the deaths of President, Vice President, the Speaker of the House, the President pro tempore of the Senate, and the secretaries of State, Treasury, and Defense, and the Attorney General? (1 pt)
\item A receipt from Bonaparte's Retreat, signed by the owner Bill (15 pts)
\item A team member adequately prepared to ward off and to destroy a vampire (13 pts)
\item A team member simulaneously using a Thighmaster{\texttrademark}, Abdomizer{\texttrademark}, and Step \& Slide{\texttrademark}, while wearing shiny spandex (40pts)
\item Someone with their eyebrows dyed two different colors (7 pts)
\item A unbroken one gallon glass milk bottle, with a team member kneeling on a stool at least three feet above and able to drop seven out of ten wooden clothespins into it (20 pts)
\item The Whitewater situation represented through interpretive dance (14 pts)
\item A styrofoam cup from Zink Building Supply in Louisville (44 pts)
\item 3 team members to place bocce using cantaloupe (12 pts)$\dagger$
\item What kind of tree is growing out of the roof of the Decatur Counter, Indiana courthouse? (7 pts)
\item Federal Express University of Chicago memorabilia to David Letterman at The Late Show, 1697 Broadway, New York, NY 10019 (212) 975-7247, bring Federal Express airway bill reciept as proof (20 pts, 80 pts extra if your team name is mentioned on the Friday, May 6th show)
\item A police care with the Denver Boot attached to the front wheel (85 pts)$\dagger$
\item An athletic sock \underline{stuffed} with dryer lint (21 pts)
\item A ship in a bottle (14 pts)
\item Pick a given lock, you will have 5 minutes (30 pts)
\item Artificial insemination (16 pts)
\item A billiard ball signed by Dawn Clark Netsch (60 pts)
\item Three bowls of porridge, one too hot, one too cold, and one just right (9pts)
\item A box of Thin Mints {\texttrademark} girl scout cookies, unopened (20 pts)
\item How do you make a Venetian blind? (5 pts)
\item A hot poker (17 pts)
\item A Lester Gay for Sheriff sign (20 pts)
\item A quagmire (8 pts)
\item The source of the following quotation: ``And where is that band who so vauntingly swore/ That the havoc of war and the battle's confusion,/ A home and a country should leave us no more!/ Their blood has washed out their foul footsteps' pollution.'' (2 pts)
\item A Cabbage Patch Kid{\texttrademark} with original birth certificate (16 pts)
\item A tick (5 pts)
\item A icicle at least 20'' long (25 pts)$\dagger$
\item What is author Steven King's blood type (4 pts)
\item A Velvet Elvis (33 pts)
\item A Vacu-Trim{\texttrademark} (30 pts, 40 points to trim your hair with it)
\item A Don Johnson CD (10 pts)
\item What is the slogan of Osgood, IN? (6 pts)
\item A Snoopy(R) Sno-cone machine (14 pts)
\item Andirons (17 pts)
\item One piece of plastic for each recycling category 1 through 7, plastic must have embossed category number (28 pts)
\item What is currently playing and coming soon to the Damm Theater? (5 pts)
\item A Peter Meter{\texttrademark} (12 pts)
\item An electric, restroom hand dryer (39 pts)
\item Where is Harold Washington buried? (2 pts)

%page 4
\item Bluegrass (10 pts)
\item Item to be announced during the judging
\item Volume 5, Number 5 of ``Over Fifty Magazine'' (10 pts)
\item A curmudgeon whining about the good old days when everyone was poor and life was miserable, but people were good and happy (10 pts)
\item a live rabbit from 10378 US North 421 in Bryantsburg and a business card from Kennet with his signature on it. (30 pts)
\item A skinny sweaty man in a green suit (9pts)
\item A bum, or a philosophy major (10 pts)$\dagger$
\item Team member to pogostick for at least one minute without falling off (16 pts)$\dagger$
\item According to a U. of C. PSAC publication, how did the term ``Field House'' enter the English language?
\item A female team member to have her head shaved in front of the judge while singing ``Figaro'' from the opera {\it Barber of Seville}, (25 pts if shoulder length, 50 pts if mid-back, 100 pts if down to waist)
\item A {\UofC} Professor \underline{yelling} ``yahoo!'' repeatedly for as long as it takes to judge the page (25 pts)
\item What is prohibited at the Jefferson Proving Grounds, according to the sign at the entrance? (10 pts)
\item Someone hooked on phonics (10 pts)
\item A speciment of the item banned in California [CA Reg. Title 14, Sec. 671 (c) (2) (J) 1.] (12 pts)
\item A full-sized steamroller to crush Barney (I love you, you love *splat*) (150 pts)$\dagger$
\item A welcome mat with ``Welcome'' written in a non-English language (14 pts)
\item A spigot (9pts)
\item A Windsor knot, tied in front of the judge (4 pts)
\item A matchbook from Marathon Fort Mart in Cisne, IL (11 pts)
\item A screw that you can only tighten (5 pts)
\item An unopened bag of holiday M+M's{\texttrademark} from Christmas (14 pts)
\item A team member wearing a pair of fishnet stockings with a seam up the back (22 pts)
\item How many beds is the University of Chicago Hospitals licensed for? (3 pts)
\item Superman Underoos{\texttrademark}, tops and bottoms (19 pts)
\item A blank piece of letterhead stationery from {\UofC} President's office (14 pts)
\item What does the plaque on a pillar at Gate 1 at Churchill Downs say? (10 pts)
\item The Nancy Drew{\texttrademark} mystery \#13 (13 pts)
\item A Bernoulli{\texttrademark} cartridge (20 pts)
\item A plecostamus (17 pts)
\item A stuffed animal over six feet tall (36 pts)
\item How many cages are at Johnston's Beagle Kennel in Akin, IL? (44 pts)
\item A Vermonster{\texttrademark} bowl from the store at 338 West Armitage (15 pts)
\item An envelope with 29 one-cent stamps canceled on it (11 pts)
\item Much ado about nothing (7 pts)
\item A Braille Playboy(c) (83 pts)
\item A polygraph (36 pts)
\item Underwear made entirely of safety pins, modeled by a team member (20 pts)
\item Someone wearing a pair of parachute pants and a Darth Vader{\texttrademark} helmet, break dancing (47 pts)
\item A copy of the ``Daily Racing Form'' (15 pts)
\item A Scantron{\texttrademark} machine (27 pts)
\item Which University of Chicago Faculty member had a part in {\it The Fugitive} (1993), what is his position and what part did he play in the movie? (4 pts)
\item What are the principal telescopes at Yerkes Observatory? (4 pts)
\item What is the zip code in Bedford, KY? (5 pts)

%page 5
\item ``Nun Run'': bring a nun in full habit to participate in a short foot race. This race will be conducted at 1:00 PM on the date of the judging. (100 pts for first place, descending to minimum of 25 pts)$\dagger$
\item A male made up at Tammy Faye Baker (make it convincing!) (16 pts)
\item Where is the Harold Washington Tree located, why was it been named as such? (4 pts)
\item A team mamber to place 20 consecutive squirts of Binaca{\texttrademark} Gold under their tongue (20 pts)
\item A map of Land Between the Lakes stapled to a Land-o-Lakes box (24 pts)
\item A person wearing a much clothing as possible, clothing normally worn as a pair is counted as one item (1 pt per item, max. 100 pts)
\item Someone wearing a full martial arts uniform to obliterate a watermelon with their bare hands (26 pts)$\dagger$
\item What is the key ingrediant in the drink ``A Screaming Viking''? (2 pts)
\item Someone dressed as the Morton Salt girl in a salt shower, must have yellow raincoat and umbrella, ``When it rains, it pours'' (21 pts)$\dagger$
\item Braided armpit hair (13 pts)
\item A team member with the entire page \# 1253 or \# 1289 from the Ameritech Pages Plus (R) for Chicago (white pages), issued August 1993, written on their exposed skin (101 pts)
\item A live peacock (35 pts)$\dagger$
\item A full-sized hook and ladder fire truck with at least two firemen and a Dalmatian (150 pts, 5 pts extra is siren is on and ladder is raised)$\dagger$
\item A plumber's helper (12 pts)
\item What is the recipe for the ``Neiman-Marcus Cookie''? (5 pts)
\item Express written consent from Major League Baseball (R) (27 pts)
\item A photocopy of a \$5,000 United States Federal Reserve note (15 pts)
\item The obituary of a living person (4 pts)
\item Who made the restoration of the Lincoln Heritage House in Elizabethtown possible? (16 pts)
\item Tang{\texttrademark} (11 pts)
\item A price quote from Elmo's on Cottage Grove for having a tombstone carved with the inscription ``Genghis Kraken, Thanks for the Herring, Sorry about your Brain,''{\dots}remember, before-U-go, call Elmo (20 pts)
\item A Sybaris(R) brochure (9 pts)
\item A Farrah Fawcett t-shirt (15 pts)
\item A shoe size 19 or larger (19 pts)
\item A copy of ``Nuvo'' from Indianapolis (5 pts)
\item Three orange whips (17 pts)
\item What is written on the Everyly Brother monument? (7  pts)
\item A bucket of poison ivy, at least 2 gallons (23 pts)
\item A left-handed deck of cards (11 pts)
\item A team member stepping on blue suede shoes (14 pts)
\item A haiku about the Bobbits (12 pts)
\item An FBI wanted poster (45 pts)
\item A dentist-office laminated poster of a cutaway diagram of a tooth (32 pts)
\item A clay pigeon (13 pts)
\item Someone bort on February 29th, with birth certificate (29 pts)
\item A fencepost hole digger (10 pts)
\item A ``magic'' eight ball to determine the points of this item
\item When was the Elizabethtown-Hardin County time capsule sealed? (4 pts)
\item A cleaver in any Menudo Album (19 pts)
\item A private dick (12 pts)
\item If the play is the tragedy of man, who is the hero? (1 pts)
\item An orange traffic cone with 2 reflective stripes on it (15 pts)
\item Miss Illinois, any year, with sash (80 pts)
\item Why did Bill Clinton have astro-turf in the back of his El Camino? (1 pt)

%page 6
\item A female team member who can tie a cherry stem in knot with her tongue, bring your own cheery. (20 pts)
\item Who is directed to the right lane at the entrance to the United States Federal Penitentiary in Marion? (15 pts with good behavior)
\item An abacus, a slide rule, and a calculator, and someone to operate all three, judges will provide a different problem to be solved using each one (25 pts)
\item A business card from the feed store at US 148 \& US 149 (This also might be a good place to pick up some rabbit food{\dots}) (9 pts)
\item What is George Lucas' dog's name? (2 pts)
\item Someone to fill their shoes with Cheez Whiz{\texttrademark} and put their feet in them, sauerkraut in their pockets, and an oyster in each ear (24 pts)
\item A sneeze (7 pts)$\dagger$
\item A backflip (11 pts)
\item 10 spoons simultaneously hangin from the team members' faces (10 pts)
\item A person smoking a whole pack of cigarettes at once (20 pts)$\dagger$
\item A dog that comes when being called, ``Iamanasshole'' (19 pts)$\dagger$
\item A plastic lobster and a pair of dentures suspended in Jello{\texttrademark} (26 pts)
\item A good-looking prosthetic nose on each cheek (19 pts)
\item A pommel horse (70 pts)
\item An eviction notice (31 pts)
\item A bad date (8 pts)
\item A Bob Greene column that  has nothing to do with Michael Jordan (7 pts)
\item A crankshaft (27 pts)
\item A small mirror, a razorblade, a dollar bill, and a Darryl Strawberry baseball card (15 pts)
\item A {\UofC} report card with the three grades D, W, and I (21 pts)
\item A popcorn ball at least 6 feet in circumference (44 pts)
\item A free spirit (10 pts)
\item Without parole, when would Richard Speck have been scheduled to be released from prison? (4 pts)
\item A glass eye (23 pts)
\item A psychiatry license (0 or 6 pts -- whatever feels good to you)
\item Who from NBC donated to the statue of Superman in Metropolis, and how many brick record donations? (27 pts)
\item A frisbee and cup from MAB's ``Rock the Quads'' concert last spring (16 pts)
\item Anything with the {\it logo} ARA Leisure Services (16 pts)
\item According to historical markers in historic downtown Paducah, how did Dr. Reuben Saunders halt the plague in Paducah and how much was Paducah worth in 1827? (17 pts)
\item An alewife necklace (modeled, of course) (27 pts)
\item A complete copy of the article where the {\UofC} social life was listed as \#300 (14 pts)
\item A horseshoe magnet (11 pts)
\item A Wienermobile{\texttrademark} whistle (15 pts)
\item A packet of Royco chicken flavoring (15 pts)
\item Copy of the Congressional Obscenity Report (14 pts)
\item A Natural Gas Scratch \& Sniff Consumber Education Card (29 pts)
\item Something old, something new, something borrowed, something blue (5 pts)
\item Two males to play a two minute game of Cat's Cradle (10 pts)
\item A refrigerator magnet from the Super Museum (10 pts)
\item A Jehovah's Witness with a copy of the Watchtower (C) (18 pts)
\item A replica of the Picasso at Daley Center, made of Spam{\texttrademark} and Q-tips{\texttrademark}, and a team member to eat it, not the Q-tips{\texttrademark} (40 pts)
\item A copy of the Effingham Daily News for a day during the hunt with the crossword puzzle completed (25 pts)
\item Machismo (5 pts)
\item What isthe modern day name of Rinaldo Street? (3 pts)

%page 7
\item Someone laughing milk through their nose (7 pts)
\item A bag of sand equal in weight to a team member, you provide the scale (30 pts)$\dagger$
\item A team member to jump rope using licorice, and then eat the licorice (18 pts)
\item Someone with their fingers sewn together (12 pts)
\item Someone with some part of their body pierced that is not their ears,  nose, or navel (15 pts)
\item A live free range chicken (30 pts)$\dagger$
\item A chainsaw (40 pts)
\item A television listing from another country (11 pts)
\item A swallow (African or European) and a coconut (8 pts)
\item An interesting anagram of ``The University of Chicago'' (0-9 pts, judge's discretion)
\item A single pen that can write in more than six different colors (7 pts)
\item A notarized copy of the List (8 pts)
\item A business brochure from Indianapolis Heliport (15 pts)
\item Where was the miniature Statue of Liberty in West Frankfort made? (8 pts)
\item A letter or message from a member of the United States Senate or House of Reps. wishing your team luck in the scavenger hunt (18 pts)
\item Two people who have birthdays on the same day of the year, with proof (8 pts)
\item A rap version of Poe's ``The Raven'' (22 pts)
\item A prosthetic arm (32 pts)
\item How many chimney are on the Wolcott house designed by T. Lilly of Chicago in Wolcott, IN? (5 pts)
\item A team member in scuba gear (29 pts)
\item What music video features a likeness of Harrison Ford being hanged?
\item A demonstration dessert tray (16 pts)
\item Something \underline{really} bizarre (this List does not qualify nor does anything on it--make it good for the points) (11 pts)
\item What Hyde Park building has an ``authentic piece'' of Plymouth Rock? (3 pts)
\item Valid drivers' licenses from the Nutmeg State, the Gem State and the Pelican State (18 pts)
\item Bubblegum flavored yogurt (14 pts)
\item An Oriental rug, must be at least 5' x 7' (35 pts)
\item A hookah (17 pts)
\item Brenda, Kelly, Andrea, Donna, Dylan, David, Steve and Brandon, whom has slept with whom, whom has almost slept with whom? (4 pts)
\item What is James Whitcomb doing with his right hand, at the Soldiers' and Sailors Monument, in Indianapolis? (5 pts)
\item A description of the tatoo on Cher's butt (5 pts)
\item A lazy susan (14 pts)
\item What color is the mailbox in front of the post office in Wayne City? (3 pts)
\item A Buddha statue (8 pts)
\item What do the Chicago telephone exchanges 445 and 238 stand for? (3 pts)
\item Create a device no larger than 1 foot in any dimension out of 8 1/2 x 11 copy paper and tape that will successfully hold a raw egg without breaking. This device will be dropped from the third floor of Ida Noyes during judging. (25 pts)
\item A rubbing of the historical marker at the entrance to the U.S. Bullion Depository in Fort Knox (15 pts)
\item A team member to recite, from memory, the name of every house in the University housing system and the resident heads or masters of each (50 pts)
\item A fat lady in a horned Viking-style helmet, singing opera (10 pts)
\end{enumerate}

$\dagger$ outside item
